### 2016-09-30 assumptions.tex
Fix overflow (assumptions)

% TODO: What can we do about the overflowing text here?
Some of the common assumptions that SymPy allows are \texttt{positive},
\texttt{negative}, \texttt{real}, \texttt{nonpositive}, \texttt{integer},
\texttt{prime} and \texttt{commutative}.\footnote{SymPy assumes that two
  expressions $A$ and $B$ commute with each other multiplicatively, that is,
  $A\cdot B=B\cdot A$, unless they both have \texttt{commutative=False}. Many
  algorithms in SymPy require special consideration to work correctly with
  noncommutative products.} Assumptions on any object can be checked with the
\verb|is_|\texttt{\textit{assumption}} attributes, like \verb|t.is_positive|.

>>>>

Some of the common assumptions are
\texttt{negative}, \texttt{real}, \texttt{nonpositive}, \texttt{integer},
\texttt{prime} and \texttt{commutative}.\footnote{SymPy assumes that two
  expressions $A$ and $B$ commute with each other multiplicatively, that is,
  $A\cdot B=B\cdot A$, unless they both have \texttt{commutative=False}. Many
  algorithms in SymPy require special consideration to work correctly with
  noncommutative products.} Assumptions on any SymPy object can be checked with the
\verb|is_|\texttt{\textit{assumption}} attributes, like \verb|t.is_positive|.
